(Working Title) Properties of the \KT\ Campaign 1 Planets, False Positive Probabilities, and Confirmation of $N$ Systems. You Were Warned: it's a Working Title.

### 2015-02-27 ms.tex
notes

This is Dan?

@@

\subsection{Others? Really bright ones amenable to followup?}

>>>>

This is Dan.

(Include comment here about how the planet parameters assume no dilution. 
Except for the two that we have AO detected binaries for, probably?
Brendan should have us flux ratios by the end of the day.
In those cases, I suppose we need to include planet properties in both cases
in which the transit is around either the more or less massive star.)

@@

\subsection{Systems Orbiting Bright Stars}
